\documentclass{article}

\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage{multicol}
\usepackage{paralist}
\usepackage{datetime}
\usepackage{hyperref}

\newdateformat{monthyeardate}{%
	\monthname[\THEMONTH], \THEYEAR}

\titleformat{\section}
{\bfseries\large}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\bfseries}
{}
{0em}
{}


\renewcommand{\maketitle}{
	\begin{center}
		{\huge\bfseries\theauthor}
		
		\vspace{.5em}

		burntfurniture@gmail.com

		443-516-6830

		\href{https://github.com/spiritualhost}{Github -- spiritualhost}
	\end{center}
}


\pagenumbering{gobble}

\begin{document}

\noindent

\author{Ryan Piazza}

\maketitle

\section{Technical Skills}

\subsection{System Administration}
\vspace{-1em} %Huge space here otherwise

\begin{multicols}{2}
	\begin{compactitem}
		\item Active Directory Management
		\item Github Management
		\item Fundamental Network Security (Sophos)
		\item Virtualization (VMware vSphere, VirtualBox, KVM/QEMU)
		\item Operating System Management
		\item VPN Setup
		\item Encryption (PGP and Bitlocker)
		\item Machine Learning (OpenAI API, Ollama)
		\item Cryptocurrency Wallets (Electrum)
		\item PC Hardware and Construction
		\item Mobile Device Management (NinjaOne)
		\item Ticketing Systems (GLPI)
	\end{compactitem}
\end{multicols}

\subsection{Programming}

Python, C++, SQL

\subsection{Scripting} 

Bash, Powershell

\subsection{Markup}

LaTex, HTML, CSS, R Markdown


\section{Job Experience}

\subsection{IT Specialist - Rollins Data Systems}
\textbf{March 2025 - \monthyeardate\today} - Daily management of IT infrastructure at a nationwide caging and donor relations company. Security through Sophos Firewall, Active Directory, Wazuh monitoring, and GLPI ticketing. Assistance of remote workers with vSphere Windows environments. Physical security setup (RFID door scanners, security cameras, WAP placement). PCI redaction assistance. 

\subsection{Escrow Accountant - EngageUSA}
\textbf{February 2024 - March 2025} - Managed daily book balancing for nationwide non-profit organizations, ranging from political action committees to animal rights organizations. Resolved discrepancies in data with caging team, improving accuracy of donor information in database. Administered payroll for mid-sized restaurant and political action committee, ensuring compliance with timekeeping and deductions. Prepared yearly tax forms. Initiated wire and ACH transfers.  

\section{Education}

\subsection{College} \textbf{June 2019 - December 2023}
Attended the University of Maryland, Baltimore County, graduating in 2023 with a B.S. in Financial Economics. 

\subsection{Certifications}

Sophos Firewall Engineer Certification. Currently studying for the Comptia A+. 

\end{document}